---
title: "BiosprayTech 2023"
author: "Xavier Delpuech, IFV, UMT EcoTech 2023"
date: "2023-09-05"
format: html
---

This map @fig-map_design is interactive, you can choose the visibility of each layer (click on the left). See below for explanations of experimental treatments.

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Map of BiosprayTech experimenal field"
#| label: fig-map_design
#| column: page

# libraries ---------------------------------------------------------------
library(sf) # (Spatial Feature) est dédié à la manipulation, la transformation et l’analyse de données spatiales. A la manière du Tidyverse, il combine les fonctionnalités de {sp}, {rgeos} et {rgdal} dans un package.
library(tidyverse) # manipulation des données
library(tmap) #(thematic map) est quant à lui dédié à la visualisation des données spatiales. Cette fois-ci, à la manière du package {ggplot2}.

# load data ---------------------------------------------------------------
# shapefile with xpdesign (each segment as a trt)
file_path <- "C:\\Users\\xdelpuech\\OneDrive - vignevin.com\\AE3\\ProjetsEnCours\\BIOSPRAYTECH\\04_TRAVAIL_EN_COURS\\2023\\RScript\\generate_modulation_map\\maps\\xpdesign2023-05-11.shp"
segment <- sf::read_sf(file_path)

unit_xp <- segment %>%
  filter(expe==1)

block <- segment %>%
  filter(!is.na(bloc)) %>%
  mutate(block = paste("block",bloc)) %>%
  group_by(block) %>%
  summarize(block=unique(block)) %>%
  sf::st_convex_hull()

rows <- segment %>%
  mutate(row = Num_rang) %>%
  group_by(row) %>%
  summarize(row=unique(row))

### modulation map
## modulation map
modu_map_path <- "C:\\Users\\xdelpuech\\OneDrive - vignevin.com\\AE3\\ProjetsEnCours\\BIOSPRAYTECH\\04_TRAVAIL_EN_COURS\\2023\\RScript\\generate_modulation_map\\maps\\modulation_map_DV76_2023-04-14.shp"
modu_map <- sf::read_sf(modu_map_path)

# affichage ----------
tmap_mode("plot")
mymap <- #tm_tiles() leaflet::providers$OpenStreetMap,group="OpenStreetMap") + 
  tm_shape(rows) + tm_lines(col="green3",lwd=2)  + 
  tm_shape(block) + tm_polygons(alpha=0,lwd=1) + tm_text("block") +
  tm_shape(unit_xp) + tm_lines(col="trt",lwd=4)  +
  tm_shape(modu_map) + tm_polygons(alpha=0.5) + tm_legend(title="Experimental design map") +  
  tm_basemap("OpenStreetMap.France",alpha=0.5) +
  tm_view(set.zoom.limits = c(18,22))
 
mymap <- tmap::tmap_leaflet(mymap) 
widgetframe::frameWidget(mymap,width="100%")
```

In this experiment, 2 factors were tested @tbl-treatments :

-   the dose of phytosanitary products : from 0.7 to 2x the reference dose (1N)

-   the spray pattern :

    -   FpF : face per face, both sides of the grapevine row received spray directly

    -   Uf : only one side of the row received spray directly

    -   BH : both sides of the row received spray directly, and the spray is oriented from bottom to top with higher dosage in the bunches area

```{r}
#| echo: false
#| warning: false
#| tbl-cap: Number of replicates per experimental treatment
#| label: tbl-treatments

# table
segment$sprayPattern <- gsub("_.*$","",segment$trt)  
segment$dose <- paste(gsub(".*_","",segment$trt),"N",sep="")

tbl_trt <- segment %>%
  filter(expe == 1) %>%
  sf::st_drop_geometry() %>%
  group_by(sprayPattern,dose) %>%
  summarize(rep=n()/4) %>%
  # Change the orientation of the table so that dose become the variable headings
  pivot_wider(names_from = dose, values_from = rep)
 
# Create table to present the data]
tbl_trt %>%
  knitr::kable(format="html",escape="F",caption="Number of replicates per experimental treatment")


```
